%Introduction
\section{Introduction}

In this paper we propose a protein function prediction algorithm,
which in essence works similarly to the adage ''Tell me who your
friend are, and I will tell you who you are''. Imagine that we can
accurately predict the function of a protein in the cells of an
organism bases on its biochemical interactions with the other
proteins, and the interactions of the other proteins between
themselves. This has in fact demonstrated to be true by
\textcite{schwikowski2000network}. But we are trying to improve on
it. In the formulation of the adage above, We want to tell you who
you are based on information on some friends of your friends. 
We want that because in the world of protein research, there are
still many that are unresearched or mostly unresearched.

The specific problem we are dealing here, from the perspective of
bioinformaticians, is of protein function prediction in a
protein-protein interaction network (PPIN), yet the actual algorithm
is more general and applies to any network really. For this reason
why we call the problem 'Partially labeled classification' (PLC) as it was
named by \textcite{szummer2002partially}.

Our proposed algorithm uses the network propagation method of random
walk with restart (RWR). These methods has been used most famously
by Google for their search algorithm but also in bioinformatics  for
example for 'disease module identification' by
\cite{vandin2012discovery, barel2020netcore}.

We wanted to make this paper somewhat self contained and therefore
we included the mathematical background of stochastic matrices and random walk
with restart in the first 2 sections as well as in the 3 appendices.
The are intended to provide a 'feel' for the RWR process,
as well as to 
intercept some possible questions, likely even by the author
within a few decades from now, about random walks and stochastic matrices.
%We dedicate sections 2 and 3 of this Thesis to explain the
%underlying mathematical theories of stochastic matrices and random
%walk with restart in graphs. 
These sections are largely going according to textbooks
from \textcite{meyer2000matrix} and \textcite{herstein_winter_1989}.
%The purpose is to make this work somewhat self standing with the
%mathematical foundations it is based on, to give a 'feel' for how
%RWR actually work, 
We included some 
lemmas that prove why we can use RWR it in the networks we are dealing
with. These two sections are expanded by appendices 1 and 2.

Section 4 deals with the subjects
of community structure and spectral clustering in graphs. There is
a great deal of overlap between the PLC problem and community structure. 
Essentially the function prediction algorithm is based on the
paradigm that proteins of the same functional classification do tend
to form 'communities' within the PPI. We therefore first propose and
test a heuristic for graph clustering, because if it doesn't work
there is no reason that our approach has any hope resolving the PLC.
We also provide in appendix 3 some details about spectral clustering
and compare it with the heuristic.

In section 5 we propose an algorithm for protein function prediction
(or more generally for the partially labeled classification
problem). We try and compare several clustering methods and then
carry forward more test with the method of choice.

Finally in section 7 we draw some conclusions, discuss other
methods and approaches, and consider possible ways to carry with
this research forward.
